---
title: "Preliminary analysis: NAT2 and propensity scores"
author: "Gustavo"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: paper
    highlight: tango
    number_sections: false
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(WeightIt)
library(survey)
library(cobalt)
library(readxl)
library(sjPlot)
library(logistf)
library(kableExtra)
library(compareGroups)
```

<style type="text/css">
.main-container {
  max-width: 1000px;
  margin-left: auto;
  margin-right: auto;
}
</style>

# Overall {.tabset} 

<div id="quarterly-product" class="section level7">

```{r}
set.seed(1)

path <- 'C:/Users/amorigg1/OneDrive - VUMC/Documents/RePORT/Digna/'
dd <- read.csv(paste0(path, 'David_Hass/2022_7_10_REPORT_Brazil.csv')) %>%
  dplyr::select(-afr, -ame, -eur)
dd_extra_info <- read.csv(paste0(path, 'dataset_AE_DrugConc_1row_per_patient_v3.csv')) %>%
  rename(afr = AFR,
         eur = EUR,
         ame = AME)

dd_final <- dd %>%
  left_join(dd_extra_info %>%
              mutate(FID = toupper(subjid)) %>%
              dplyr::select(FID, alcoholhx_bsl, smokhx_bsl, drughx_bsl,
                            afr, eur, ame)) %>%
  mutate(nat2_cat = dd$nat2_3lev,
         sex = as.factor(sex),
         hgapct_group = ifelse(is.na(lab_hgapct), NA,
                               ifelse(lab_hgapct < 5.7, '5.7-',
                                      ifelse(lab_hgapct < 6.4, '5.7-6.4', '6.5+')))) %>%
  filter(!is.na(nat2_3lev) & tb_standard==1) %>%
  filter(!is.na(afr)) %>%
  filter(!is.na(dot_yesno) & !is.na(lab_hgapct) & !is.na(hiv)) %>%
  mutate(nat2_cat = ifelse(nat2_3lev == 3, 'slow',
                            ifelse(nat2_3lev == 2, 'intermediate', 'extensive')),
         #nat2_cat = relevel(as.factor(nat2_cat), ref = 'extensive'),
         nat2_cat = relevel(as.factor(nat2_cat), ref = 'extensive'),
         nat2_bin = ifelse(nat2_3lev == 3, 1, 0), ## intermediate/extensive
         alcoholhx_bsl = ifelse(is.na(alcoholhx_bsl), NA,
                                ifelse(alcoholhx_bsl %in% 'never', 0, 1)),
         alcoholhx_bsl = as.factor(alcoholhx_bsl),
         smokhx_bsl = ifelse(is.na(smokhx_bsl), NA,
                             ifelse(smokhx_bsl %in% 'never', 0, 1)),
         smokhx_bsl = as.factor(smokhx_bsl),
         drughx_bsl = ifelse(is.na(drughx_bsl), NA,
                             ifelse(drughx_bsl %in% 'never', 0, 1)),
         drughx_bsl = as.factor(drughx_bsl),
         bmi = weight/(height/100)^2,
         any_hepatic_all = 1*(any_hepatic_all == 1),
         any_hepatic_relatedtb = 1*(any_hepatic_relatedtb == 1))

outcomes <- c('ever_ae_all', 'ever_ae_relatedtb', 'ever_grade345_all', 'ever_grade345_relatedtb',
              'ever_hepatic_all', 'ever_hepatic_all', 'ever_hepatic_relatedtb', 'fail_recur')
exposure <- c('nat2_bin', 'nat2_cat')
covariates_out <- c('hiv', 'age', 'sex', 'dot_yesno', 'lab_hgapct', 'afr', 'eur')
covariates_out_v2 <- c('hiv', 'age', 'sex', 'afr', 'eur')
covariates_ps  <- c('hiv', 'age', 'sex', 'dot_yesno', 'lab_hgapct', 'bmi',
                    'alcoholhx_bsl', 'smokhx_bsl', 'drughx_bsl')
```


```{r}
run_mod <- function(i, j, data, B = B, boots_ci = FALSE,
                    outcomes, exposure,
                    covariates_ps, covariates_out){
  out_var <- outcomes[i]
  exp_var <- exposure[j]
  
  out_eq  <- as.formula(paste0(out_var, ' ~ ', exp_var))
  out_ps  <- as.formula(paste0(exp_var, ' ~ ', paste0(covariates_ps, collapse = ' + ')))
  out_all <- as.formula(paste0(out_var, ' ~ ', paste0(c(exp_var, covariates_out), collapse = ' + ')))
  
  if (j == 1){
    weights_ps <- weightit(out_ps, data = data)
  } else {
    weights_ps <- weightit(out_ps, data = data, estimand = "ATT", focal = levels(data[,exp_var])[1])
  }
  data$wts <- weights_ps$weights
  
  des  <- svydesign(id = ~NULL, data = data, weights = ~wts)
  fit0 <- glm(out_eq, data = data, family = binomial)
  fit1 <- svyglm(out_eq, design = des, family = binomial) 
  fit2 <- glm(out_all, data = data, family = binomial)
  fitwt <- logistf(out_eq, data=data, weights=wts)

  fit1_coef <- fit2_coef <- NULL
  if (boots_ci){
    fit1_coef <- matrix(NA, ncol = j+1, nrow=B+1)
    fit1_coef[1,] <- fit1$coefficients
    
    fit2_coef <- matrix(NA, ncol = j+1, nrow=B+1)
    fit2_coef[1,] <- fitwt$coefficients
    
    ncases    <- sum(data[,out_var] & data[,exp_var]=='extensive')
    ncontrols <- sum(data[,out_var]==0 | data[,exp_var]!='extensive')
    for (b in 2:(B+1)){
      data_temp <- data[sample(1:nrow(data), nrow(data), replace = TRUE),]
#      samp_cases <- sample(which(data[,out_var]==1 & data[,exp_var]=='extensive'), ncases, replace = TRUE)
#      if (length(which(data[,out_var]==1 & data[,exp_var]=='extensive')) == 1)
#        samp_cases <- which(data[,out_var]==1 & data[,exp_var]=='extensive')
#      samp_controls <- sample(which(data[,out_var]==0 | data[,exp_var]!='extensive'), ncontrols, replace = TRUE)
#      data_temp <- data[c(samp_cases,samp_controls),]
      des_temp  <- svydesign(id = ~NULL, data = data_temp, weights = ~wts)
      fit1_coef[b,] <- svyglm(out_eq, design = des_temp, family = binomial)$coef
      fit2_coef[b,] <- logistf(out_eq, data=data_temp, weights=wts)$coef
    }
    colnames(fit1_coef) <- names(fit1$coefficients)
    colnames(fit2_coef) <- names(fitwt$coefficients)
  }
  
  return(list(mod_all = fit2, mod_ps = fit1, mod_null = fit0, weights_ps = weights_ps, mod_firth = fitwt,
              out_var = out_var, exp_var = exp_var, ps_wgts = weights_ps, fit1_coef_boots = fit1_coef, fit2_coef_boots = fit2_coef))
}
```

```{r}
summary_tab <- function(x) {
  ci95 <- round(exp(confint.default(x)), 2)
  data.frame(OR = round(exp(summary(x)$coef[,1]), 2),
             CI = paste0('(', ci95[,1], ' ; ', ci95[,2], ')'),
             p.value = round(summary(x)$coef[,4], 3)) %>%
  kable() %>% kable_styling()
}

summary_tab_profile <- function(x) {
  ci95 <- round(exp(confint(x)), 2)
  ci95 <- round(exp(confint(x)), 2)
  data.frame(OR = round(exp(summary(x)$coef[,1]), 2),
             CI = paste0('(', ci95[,1], ' ; ', ci95[,2], ')'),
             p.value = round(summary(x)$coef[,4], 3)) %>%
  kable() %>% kable_styling()
}

summary_ps_tab <- function(x, mod) {
  if (ncol(mod$fit1_coef_boots) == 3) {
      ci95 <- rbind(exp(quantile(mod$fit1_coef_boots[,1], probs = c(0.025, 0.975))),
                exp(quantile(mod$fit1_coef_boots[,2], probs = c(0.025, 0.975))),
                exp(quantile(mod$fit1_coef_boots[,3], probs = c(0.025, 0.975))))
  } else {
      ci95 <- rbind(exp(quantile(mod$fit1_coef_boots[,1], probs = c(0.025, 0.975))),
                exp(quantile(mod$fit1_coef_boots[,2], probs = c(0.025, 0.975))))
  }
  ci95_boots <- round(ci95, 2)
  ci95_ps    <- round(exp(confint.default(x)), 2)
  data.frame(OR = round(exp(summary(x)$coef[,1]), 2),
             #CI_conservative = paste0('(', ci95_ps[,1], ' ; ', ci95_ps[,2], ')'),
             CI_bootstrap    = paste0('(', ci95_boots[,1], ' ; ', ci95_boots[,2], ')')) %>%
  kable() %>% kable_styling()
}



summary_firth_tab <- function(x, mod) {
  if (ncol(mod$fit2_coef_boots) == 3) {
      ci95 <- rbind(exp(quantile(mod$fit2_coef_boots[,1], probs = c(0.025, 0.975))),
                exp(quantile(mod$fit2_coef_boots[,2], probs = c(0.025, 0.975))),
                exp(quantile(mod$fit2_coef_boots[,3], probs = c(0.025, 0.975))))
  } else {
      ci95 <- rbind(exp(quantile(mod$fit2_coef_boots[,1], probs = c(0.025, 0.975))),
                exp(quantile(mod$fit2_coef_boots[,2], probs = c(0.025, 0.975))))
  }
  ci95_boots <- round(ci95, 2)
  ci95_ps    <- round(exp(confint.default(x)), 2)
  data.frame(OR = round(exp(coef(x)), 2),
             #CI_conservative = paste0('(', ci95_ps[,1], ' ; ', ci95_ps[,2], ')'),
             CI_bootstrap    = paste0('(', ci95_boots[,1], ' ; ', ci95_boots[,2], ')')) %>%
  kable() %>% kable_styling()
}
```


## Overview {.tabset}

### Models

<br>

Four models will be computed for each outcome:

1. Univariable model, adjusting for NAT2 only
2. Full model, adjusting for all covariates: `r covariates_out`
3. Propensity score weighted, it is the univariable model weighted by the propensity score
4. Weighted Logistic regression with firth correction, where the weights are propensity scores

- The propensity score model regresses the exposure NAT2 on the following covariates: `r covariates_ps`.
  - We used a multinomial model to estimate the propensity score, since NAT2 contains 3 categories: `r levels(dd_final$nat2_cat)`.
  - Then, the predicted (estimated) propensity score is used as weights in the main outcome regression model.
  - The goal is avoid overfitting, which may happen if we include all covariates in the main outcome regression model.

**Note 1:**

- For the binary exposure (binary NAT2), we used a logistic regression model to estimate the propensity score.
- The binary exposure was used because some levels of NAT2 is almost empty, which could lead to difficulties during the estimation process. 

**Note 2:**

- Firth correction was used because some levels of NAT2 are nearly empty.
- Firth correction is used when there's separation in the data, i.e., when the outcome is separates the exposure perfectly. In our case, some levels of NAT2 is nearly empty, causing a separation and issues with standard logistic regression. Firth correction, although originally created to reduced biases in logistic regression due to small samples, can also be used in such situations. [Here](http://fmwww.bc.edu/RePEc/bocode/f/firthlogit.html) is a reference, related to Stata.

**Note 3:**

- Both the univariable and full model uses Wald-type confidence intervals, which are based on normal approximations. However, when the sample size is small, they may be inaccurate. This is explained in the link above (section **Remarks**)
- The logistic regression with propensity score weights use Bootstrap with 999 replicates to construct (a quantile) confidence intervals.
- The logistic regression with firth correction uses the profile likelihood to construct confidence intervals; they may be more accurate (than Wald-type CIs) when the sample size is small.


### Table

<br>

Summary data by HIV status (1 = HIV-seropositive, 0 = HIV-seronegative)

```{r}
B <- 999 ## Bootstrap replicates

dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0('hiv ~ ', paste(c(exposure, union(c(covariates_out[-1], 'ame', 'hgapct_group'), covariates_ps[-1]), outcomes), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


























## Binary exposure {.tabset}

### Overal AE {.tabset}

#### Outcome: `r outcomes[1]`: {.tabset}

```{r}
res <- run_mod(i=1, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

ps_weights_bin <- res$weights_ps$weights

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[1], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```

##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```







#### Outcome: `r outcomes[2]`: {.tabset}

```{r}
out_i <- 2
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```


##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```






#### Outcome: `r outcomes[3]`: {.tabset}

```{r}
out_i <- 3
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out_v2)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```



##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```












#### Outcome: `r outcomes[4]`: {.tabset}

```{r}
out_i <- 4
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```


##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```



##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```

##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```



### Hepatic AE {.tabset}

#### Outcome: `r outcomes[5]`: {.tabset}

```{r}
out_i <- 5
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```





#### Outcome: `r outcomes[6]`: {.tabset}

```{r}
out_i <- 6
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```



#### Outcome: `r outcomes[7]`: {.tabset}

```{r}
out_i <- 7
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```








### Fail/recurrence {.tabset}

#### Outcome: `r outcomes[8]`: {.tabset}

**1=Extensive, 0=Slow/intermediate

```{r}
out_i <- 8
dd_final$nat2_bin = ifelse(dd_final$nat2_3lev >= 2, 0, 1)
res <- run_mod(i=out_i, j=1, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
dd_final_tab$nat2_bin <- as.factor(dd_final_tab$nat2_bin)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[1], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```



##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```
























## 3-level exposure {.tabset}

### Overal AE {.tabset}

#### Outcome: `r outcomes[1]`: {.tabset}

```{r}
res <- run_mod(i=1, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[1], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```




#### Outcome: `r outcomes[2]`: {.tabset}

```{r}
out_i <- 2
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

ps_weights_3level <- res$weights_ps$weights

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```


##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```

##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```







#### Outcome: `r outcomes[3]`: {.tabset}

```{r}
out_i <- 3
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out_v2)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```



##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```













#### Outcome: `r outcomes[4]`: {.tabset}

```{r}
out_i <- 4
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```


##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```



##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```




### Hepatic AE {.tabset}

#### Outcome: `r outcomes[5]`: {.tabset}

```{r}
out_i <- 5
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```





#### Outcome: `r outcomes[6]`: {.tabset}

```{r}
out_i <- 6
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```






#### Outcome: `r outcomes[7]`: {.tabset}

```{r}
out_i <- 6
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```


##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```








### Fail/recurrence {.tabset}

#### Outcome: `r outcomes[8]`: {.tabset}

```{r}
out_i <- 8
dd_final$nat2_cat <- relevel(dd_final$nat2_cat, ref='slow')
res <- run_mod(i=out_i, j=2, data = dd_final, B = B, boots_ci = TRUE,
               outcomes = outcomes, exposure = exposure,
               covariates_ps = covariates_ps, covariates_out = covariates_out)

#bal.tab(res$ps_wgts, un=TRUE)
#bal.tab(res$ps_wgts, stats = c("m"), thresholds = c(m = 0.02))
```

##### Table

<br>

```{r}
dd_final_tab <- dd_final
for (col_i in outcomes)
  dd_final_tab[,col_i] <- as.character(dd_final_tab[,col_i])  
dd_final_tab$dot_yesno <- as.factor(dd_final_tab$dot_yesno)
dd_final_tab$hiv <- as.factor(dd_final_tab$hiv)
tab0 <- compareGroups(paste0(outcomes[out_i], ' ~ ', paste(c(exposure[2], union(c(covariates_out, 'ame', 'hgapct_group'), covariates_ps)), collapse = ' + ')),
                      data = dd_final_tab, method = 2)
tab0 <- createTable(tab0, show.all = TRUE)
export2md(tab0)
```



##### Univariable model

```{r}
#tab_model(res$mod_null)
summary_tab(res$mod_null)
```

##### Full model

**Wald-type interval**

```{r}
summary_tab(res$mod_all)
```

**Profile-likelihood type interval**

```{r}
summary_tab_profile(res$mod_all)
```


##### PS weighted

```{r}
summary_ps_tab(res$mod_ps, mod=res)
```

##### PS weighted (Firth correction)

```{r}
summary_firth_tab(res$mod_firth, mod=res)
```




```{r}
write.csv(data.frame(subjid = dd_final$FID, ps_weights_bin=ps_weights_bin, ps_weights_3level=ps_weights_3level),
          'C:/Users/amorigg1/OneDrive - VUMC/Documents/RePORT/Digna/David_Hass/ps_weights_new.csv', row.names = FALSE)
```
